Trends of downward SDR in Thessaloniki

### 2023-05-05 Article.Rmd
Commit 2023-05-05 18:17

documentclass:  article
classoption:    a4paper,oneside
fontsize:       12pt
geometry:       "left=0.5in,right=0.5in,top=0.5in,bottom=0.5in"
link-citations: yes
colorlinks:     yes
urlcolor:       blue

bibliography:   [references.bib]
biblio-style:   apalike

header-includes:
  - \usepackage{caption}
  - \usepackage{placeins}
  - \captionsetup{font=small}

output:
  bookdown::pdf_document2:
    number_sections: no
    fig_caption:     yes
    keep_tex:        yes
    latex_engine:    xelatex
    toc:             yes
    toc_depth:       4
    fig_width:       7
    fig_height:      4.5
  html_document:
    toc:             true
    fig_width:       7.5
    fig_height:      5
date: "`r format(Sys.time(), '%F')`"

>>>>

documentclass:  article
classoption:    a4paper,oneside
fontsize:       12pt
geometry:       "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
link-citations: yes
colorlinks:     yes
urlcolor:       blue
bibliography:   [references.bib]
biblio-style:   apalike
date:           "`r format(Sys.time(), '%F')`"

header-includes:
  - \usepackage{caption}
  - \usepackage{placeins}
  - \captionsetup{font=small}
  - \usepackage{setspace}\doublespacing
  - \usepackage{float}

output:  
  bookdown::pdf_document2:
    number_sections: no
    fig_caption:     yes
    keep_tex:        yes
    latex_engine:    xelatex
    toc:             yes
    toc_depth:       4
    fig_width:       7
    fig_height:      4.5
  html_document:
    toc:             true
    fig_width:       7.5
    fig_height:      5
